Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology

### 2019-09-09 reproducing_registered_reports.Rmd
changes through line 91

Researchers are currently exploring ways to make science more open and transparent. Among novel developments such as pre-registration, pre-prints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., [@morey_peer_2016]. Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work. This requires the development of new skills and best practices, since most scientists have not received training in how to make their work reproducible. It is important to evaluate how data and code are currently being shared, and how easy it is to reproduce analyses reported in the published literature, to learn what can be improved. With this goal in mind, we computationally reproduced the main results of Registered Reports published in the psychological literature.

It is desirable that research is reproducible. Data availability has the potential to make science more efficient by facilitating the re-use of data. The availability of analysis code makes it possible for peers to check and correct published findings. According to @kitzes_practice_2017, computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code needs to be shared.

@@

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article. @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*. Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time. @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software. For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. @stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.

>>>>

Researchers are currently exploring ways to make science more open and transparent. Among novel developments such as pre-registration, preprints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., [@morey_peer_2016]. Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work. This requires the development of new skills and best practices, since most scientists have not received training in how to make their work reproducible. It is important to evaluate how data and code are currently being shared, and how easy it is to reproduce analyses reported in the published literature, to learn what can be improved. With this goal in mind, we computationally reproduced the main results of Registered Reports published in the psychological literature.

It is desirable that research is reproducible. Data availability has the potential to make science more efficient by facilitating the re-use of data. The availability of analysis code makes it possible for peers to check and correct published findings. According to @kitzes_practice_2017, computational reproducibility means that ”a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.” For scientific research to be computationally reproducible, the data and code need to be shared.

@@

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the articles. @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*. Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time. @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one paper's results could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software. For the remaining articles, 32 sets of results could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. @stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.
